---
title: "Shiny App Assignment"
date: "July 20, 2021"
output:
  ioslides_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Shiny App Assignment for JHU

This is a submission for the **JHU Coursera - Developing Data Products** course. I have used the Iris data and visualized it with 2 input options --1) Sepal or Petal, and 2) Species. Per the official tutorial, I found that the latest version supports single-file app. Although the lessons were taught using 2 separate files, I tried developing the app with single file. The code does not fit in the slide. Please refer to the app file itself uploaded to the same repository for the details. 

The app is hostes on Shiny.io: 
[https://gitttykatt.shinyapps.io/jhu_shiny/](https://gitttykatt.shinyapps.io/jhu_shiny/)

The tutorial from R Studio can be found on their website: 
[https://shiny.rstudio.com/tutorial/written-tutorial/lesson1/](https://shiny.rstudio.com/tutorial/written-tutorial/lesson1/)

## app.R code - ui part

```{r, message=FALSE, eval=FALSE, echo=TRUE}

# Define UI for app that draws a visualization of Iris dataset ----
ui <- fluidPage(
  
  # App title ----
  titlePanel("Iris dataset visualization"),

  p("For JHU Coursera Assignment, July 20, 2021"),
  br(), 
  
  # Sidebar layout with input and output definitions ----
  sidebarLayout(
    
    # Sidebar panel for inputs ----
    sidebarPanel(
      
      # Input: Choices ----
      
      radioButtons(inputId = "sepalorpetal", 
                   label = "Select Sepal or Petal:", 
                   choices = list("Sepal" = "sepal", 
                                  "Petal" = "petal"), 
                   selected = "sepal"
                   ), 
      
      checkboxGroupInput(inputId = "species",
                  label = "Select Species:",
                  choices = c("Setosa" = "setosa", 
                              "Versicolor" = "versicolor", 
                              "Virginica" = "virginica"), 
                  selected = "setosa"
                  ), 
      
      br(), 
      p("More information on Iris dataset can be found on:"), 
      a("https://en.wikipedia.org/wiki/Iris_flower_data_set")
      
    ),
    
    # Main panel for displaying outputs ----
    mainPanel(
      
      # Output ----
      plotOutput(outputId = "plot")
      
    )
  )
)

```

## app.R code - server part

```{r, message=FALSE, eval=FALSE, echo=TRUE}

# Define server logic required to draw a plot ----
server <- function(input, output) {

  output$plot <- renderPlot({
    
    data <- iris
     
    if (input$sepalorpetal == "sepal") {
      data <- data %>% select(x = Sepal.Width, y = Sepal.Length, Species)
    }
    else if (input$sepalorpetal == "petal") {
      data <- data %>% select(x = Petal.Width, y = Petal.Length, Species)
    }
    
    validate(
      need(input$species != "", "Please select at least 1 Specie")
    )
    
    data %>%
      filter(Species == input$species) %>%
      ggplot(aes(x, y, col=Species)) + 
      geom_point() + 
      labs(x = "Width", y = "Length")
  }

  )
}

```

## app.R Output

```{r, message=FALSE}
library(shiny)
library(ggplot2)
library(dplyr)

# Define UI for app that draws a visualization of Iris dataset ----
ui <- fluidPage(
  
  # App title ----
  titlePanel("Iris dataset visualization"),

  p("For JHU Coursera Assignment, July 20, 2021"),
  br(), 
  
  # Sidebar layout with input and output definitions ----
  sidebarLayout(
    
    # Sidebar panel for inputs ----
    sidebarPanel(
      
      # Input: Choices ----
      
      radioButtons(inputId = "sepalorpetal", 
                   label = "Select Sepal or Petal:", 
                   choices = list("Sepal" = "sepal", 
                                  "Petal" = "petal"), 
                   selected = "sepal"
                   ), 
      
      checkboxGroupInput(inputId = "species",
                  label = "Select Species:",
                  choices = c("Setosa" = "setosa", 
                              "Versicolor" = "versicolor", 
                              "Virginica" = "virginica"), 
                  selected = "setosa"
                  ), 
      
      br(), 
      p("More information on Iris dataset can be found on:"), 
      a("https://en.wikipedia.org/wiki/Iris_flower_data_set")
      
    ),
    
    # Main panel for displaying outputs ----
    mainPanel(
      
      # Output ----
      plotOutput(outputId = "plot")
      
    )
  )
)

# Define server logic required to draw a plot ----
server <- function(input, output) {

  output$plot <- renderPlot({
    
    data <- iris
     
    if (input$sepalorpetal == "sepal") {
      data <- data %>% select(x = Sepal.Width, y = Sepal.Length, Species)
    }
    else if (input$sepalorpetal == "petal") {
      data <- data %>% select(x = Petal.Width, y = Petal.Length, Species)
    }
    
    validate(
      need(input$species != "", "Please select at least 1 Specie")
    )
    
    data %>%
      filter(Species == input$species) %>%
      ggplot(aes(x, y, col=Species)) + 
      geom_point() + 
      labs(x = "Width", y = "Length")
  }

  )
}

shinyApp(ui = ui, server = server)

```

